### 2021-07-19 chapters/results/1_results_rq1.tex
wip statistics

Figure \ref{box:clustering_all_25} displays the box-plots of the weighted mutation score obtained from each individual sample. We can observe that for every box-plot the \textit{p-value} is below 0.05 or 5\%.
Table \ref{tab:clustering_all_25} displays the results of clustering mutants with all characteristics and the number of clusters equal to the total amount of mutants* 0.25.  
The maximum and minimum differences between the score of a full set and clustered are is 3.52\% and 0.04\% respectively.  
The average of the differences between full set score and clustered score is 0.58\%.
It is also noticeable that the minimum and maximum accuracy are 50\% and 100\% respectively.
This means that there was at least one cluster that consisted of only mutants that were killed or survived.
The minimum accuracy cannot go below 50\%.
If the percentage does go below 50\% the representation of a cluster will flip from survived to killed or the other way around.

@@

Figure \ref{box:clustering_all_50} displays the box-plots of the weighted mutation score obtained from each individual sample. We can observe that for every box-plot the \textit{p-value} is below 0.05 or 5\%.
Table \ref{tab:clustering_all_50} displays the results of clustering mutants with all characteristics and the number of clusters equal to the total amount of mutants* 0.50.  
The maximum and minimum differences between the score of a full set and clustered set are 3.63\% and 0.02\% respectively.
The average of the differences between full set score and clustered score is 0.48\% which is smaller than the average difference than that of the 25\% set.

@@

Figure \ref{box:clustering_all_75} displays the box-plots of the weighted mutation score obtained from each individual sample. We can observe that for every box-plot the \textit{p-value} is below 0.05 or 5\%.
Table \ref{tab:clustering_all_75} displays the results of clustering mutants with all characteristics and the number of clusters equal to the total amount of mutants* 0.75.  
The maximum and minimum differences between the score of a full set and clustered set are 3.63\% and 0\% respectively.  
The average of the differences between full set score and clustered score is 0.48\% which is higher than the average difference than that of the 25\% and the same of that of the 50\% set.

@@

Figure \ref{box:clustering_no_distance_25} displays the box-plots of the weighted mutation score obtained from each individual sample. We can observe that for every box-plot the \textit{p-value} is below 0.05 or 5\%.
Table \ref{tab:clustering_no_distance_25} displays the results of clustering mutants without Levensthein distance and the number of clusters equal to the total amount of mutants * 0.25. 
We observe that the maximum and minimum differences in mutation score between a full set and a clustered set  3.61\% and 0.09\% respectively.
The average of the differences between full set score and clustered score is 0.53\%.

@@

Figure \ref{box:clustering_no_distance_50} displays the box-plots of the weighted mutation score obtained from each individual sample. We can observe that for every box-plot the \textit{p-value} is below 0.05 or 5\%.
Table \ref{tab:clustering_no_distance_50} displays the results of clustering mutants without Levensthein distance and the number of clusters equal to the total amount of mutants * 0.50.
The maximum and minimum differences between the score of a full set and clustered set are 3.65\% and 0.03\% respectively.
We observe that the average cluster accuracy is higher than the average cluster accuracy of the 25\% set. 
The average of the differences between full set score and clustered score is 0.49\% which is smaller than the average difference than that of the 25\% set.

@@

Figure \ref{box:clustering_no_distance_75} displays the box-plots of the weighted mutation score obtained from each individual sample. We can observe that for every box-plot the \textit{p-value} is below 0.05 or 5\%.
Table \ref{tab:clustering_no_distance_75} displays the results of clustering mutants without Levensthein distance and the number of clusters equal to the total amount of mutants * 0.50.
The maximum and minimum differences between the score of a full set and clustered set are 3.63\% and 0.04\% respectively.
We observe that the average accuracy is higher than the average accuracy of the other sets.
The average of the differences between full set score and clustered score is  0.49\% which is higher than the average difference than that of the 25\% and the same of that of the 50\% set.
\end{document}

>>>>

Figure \ref{box:clustering_all_25} displays the box-plots of the weighted mutation score obtained from each individual sample. 
We can observe that for every box-plot the \textit{p-value} is below 0.05 or 5\%.
To view the box-plots separately and in more detail see Appendix \ref{ap:full_25}.
Table \ref{tab:clustering_all_25} displays the results of clustering mutants with all characteristics and the number of clusters equal to the total amount of mutants* 0.25.  
The maximum and minimum differences between the score of a full set and clustered are is 3.52\% and 0.04\% respectively.  
The average of the differences between full set score and clustered score is 0.58\%.
It is also noticeable that the minimum and maximum accuracy are 50\% and 100\% respectively.
This means that there was at least one cluster that consisted of only mutants that were killed or survived.
The minimum accuracy cannot go below 50\%.
If the percentage does go below 50\% the representation of a cluster will flip from survived to killed or the other way around.

@@

Figure \ref{box:clustering_all_50} displays the box-plots of the weighted mutation score obtained from each individual sample. 
We can observe that for every box-plot the \textit{p-value} is below 0.05 or 5\%.
To view the box-plots separately and in more detail see Appendix \ref{ap:full_50}.
Table \ref{tab:clustering_all_50} displays the results of clustering mutants with all characteristics and the number of clusters equal to the total amount of mutants* 0.50.  
The maximum and minimum differences between the score of a full set and clustered set are 3.63\% and 0.02\% respectively.
The average of the differences between full set score and clustered score is 0.48\% which is smaller than the average difference than that of the 25\% set.

@@

Figure \ref{box:clustering_all_75} displays the box-plots of the weighted mutation score obtained from each individual sample. 
We can observe that for every box-plot the \textit{p-value} is below 0.05 or 5\%.
To view the box-plots separately and in more detail see Appendix \ref{ap:full_75}.
Table \ref{tab:clustering_all_75} displays the results of clustering mutants with all characteristics and the number of clusters equal to the total amount of mutants* 0.75.  
The maximum and minimum differences between the score of a full set and clustered set are 3.63\% and 0\% respectively.  
The average of the differences between full set score and clustered score is 0.48\% which is higher than the average difference than that of the 25\% and the same of that of the 50\% set.

@@

Figure \ref{box:clustering_no_distance_25} displays the box-plots of the weighted mutation score obtained from each individual sample.
We can observe that for every box-plot the \textit{p-value} is below 0.05 or 5\%.
To view the box-plots separately and in more detail see Appendix \ref{ap:no_distance_25}.
Table \ref{tab:clustering_no_distance_25} displays the results of clustering mutants without Levensthein distance and the number of clusters equal to the total amount of mutants * 0.25. 
We observe that the maximum and minimum differences in mutation score between a full set and a clustered set  3.61\% and 0.09\% respectively.
The average of the differences between full set score and clustered score is 0.53\%.

@@

Figure \ref{box:clustering_no_distance_50} displays the box-plots of the weighted mutation score obtained from each individual sample. 
We can observe that for every box-plot the \textit{p-value} is below 0.05 or 5\%.
To view the box-plots separately and in more detail see Appendix \ref{ap:no_distance_50}.
Table \ref{tab:clustering_no_distance_50} displays the results of clustering mutants without Levensthein distance and the number of clusters equal to the total amount of mutants * 0.50.
The maximum and minimum differences between the score of a full set and clustered set are 3.65\% and 0.03\% respectively.
We observe that the average cluster accuracy is higher than the average cluster accuracy of the 25\% set. 
The average of the differences between full set score and clustered score is 0.49\% which is smaller than the average difference than that of the 25\% set.

@@

Figure \ref{box:clustering_no_distance_75} displays the box-plots of the weighted mutation score obtained from each individual sample. 
We can observe that for every box-plot the \textit{p-value} is below 0.05 or 5\%.
To view the box-plots separately and in more detail see Appendix \ref{ap:no_distance_75}.
Table \ref{tab:clustering_no_distance_75} displays the results of clustering mutants without Levensthein distance and the number of clusters equal to the total amount of mutants * 0.50.
The maximum and minimum differences between the score of a full set and clustered set are 3.63\% and 0.04\% respectively.
We observe that the average accuracy is higher than the average accuracy of the other sets.
The average of the differences between full set score and clustered score is  0.49\% which is higher than the average difference than that of the 25\% and the same of that of the 50\% set.
\end{document}
